\begin{thebibliography}{99}

    \bibitem{fib} FIB.
    \textit{Facultad de Informática de Barcelona.} \\
    \url{https://www.fib.upc.edu/}

    \bibitem{upc} UPC.
    \textit{Portal de la Universitat Politécnica de Catalunya.} \\
    \url{https://www.upc.edu/}

    \bibitem{domo21} Domo21.
    \textit{} \\
    \url{https://www.sicma21.com/}
    
    \bibitem{kanban} Wikipedia Commons.
    \textit{Abstract Kanban Board.} \\
    \url{https://commons.wikimedia.org/wiki/File:Abstract_Kanban_Board.svg}

    \bibitem{github} GitHub.
    \textit{} \\
    \url{https://github.com/}

    \bibitem{trello} Trello.
    \textit{} \\
    \url{https://trello.com/}
    
    \bibitem{stm32wb55rg} STMicroelectronics.
    \textit{STM32WB55RG | Product.} \\
    \url{https://www.st.com/en/microcontrollers-microprocessors/stm32wb55rg.html}

    \bibitem{nucleo-wb55rg} STMicroelectronics.
    \textit{NUCLEO-WB55RG | Product.} \\
    \url{https://www.st.com/en/evaluation-tools/nucleo-wb55rg.html}
    
    \bibitem{lux-vs-wm2} EVOLUX.
    \textit{Lux vs W/m².} \\
    \url{https://evolux.cl/lux-vs-wm2}

    \bibitem{an2867} Application Note AN2867.
    \textit{Guidelines for oscillator design on STM8AF/AL/S and STM32 MCUs/MPUs.} \\
    \url{https://www.st.com/resource/en/application_note/an2867-guidelines-for-oscillator-design-on-stm8afals-and-stm32-mcusmpus-stmicroelectronics.pdf}

    \bibitem{an5042} Application Note AN5042.
    \textit{How to calibrate the HSE clock for RF applications on STM32 wireless MCUs.} \\
    \url{https://www.st.com/resource/en/application_note/an5042-how-to-calibrate-the-hse-clock-for-rf-applications-on-stm32-wireless-mcus-stmicroelectronics.pdf}
    \bibitem{an5129} Application Note AN5129.
    \textit{Guidelines for meander design using low-cost PCB antennae with 2.4 GHz radio for STM32WB/WB0 MCUs.} \\
    \url{https://www.st.com/resource/en/application_note/an5129-guidelines-for-meander-design-using-lowcost-pcb-antennae-with-24-ghz-radio-for-stm32wbwb0-mcus-stmicroelectronics.pdf}

    \bibitem{an6335} Application Note AN6335.
    \textit{MLPF-WB and MLPF-NRG PCB design guidelines and reference hardware.} \\
    \url{https://www.st.com/resource/en/application_note/an6335-mlpfwb-and-mlpfnrg-pcb-design-guidelines-and-reference-hardware-stmicroelectronics.pdf}

    \bibitem{spma056} Application Note SPMA056.
    \textit{System Design Guidelines for the TM4C129x Family of Tiva™ C Series Microcontrollers.} \\
    \url{https://www.ti.com/lit/an/spma056/spma056.pdf?ts=1767867045202}

    \bibitem{stm32_pinout} Arm Mbed.
    \textit{NUCLEO-WB55RG.} \\
    \url{https://os.mbed.com/platforms/ST-Nucleo-WB55RG/}
    
    \bibitem{impedance_calc} JLCPCB.
    \textit{Controlled Impedance Calculator.} \\
    \url{https://jlcpcb.com/pcb-impedance-calculator}
    
    \bibitem{jlcpcb_shop} JLCPCB.
    \textit{Assembly Parts Library.} \\
    \url{https://jlcpcb.com/parts/}

    \bibitem{ble_stack_github} GitHub.
    \textit{STMicroelectronics / STM32CubeWB.} \\
    \url{https://github.com/STMicroelectronics/STM32CubeWB/blob/master/Projects/STM32WB_Copro_Wireless_Binaries/STM32WB5x/stm32wb5x_BLE_Stack_full_fw.bin}
    

\end{thebibliography}